Reasoning About a Machine with Local Capabilities

### 2019-02-08 toplas/paper.tex
Resolve a TODO.

\textbf{Program start-up} We assume that the language runtime initializes the
memory as follows: a contiguous array of memory is reserved for the stack, for
which we receive a stack pointer in the register $r_\stk$. We stress that
the stack is not built-in, but merely an abstraction we put on this piece of the
memory. The stack pointer is local and has $\rwlx$ permission. Note that this
means that we will be placing and executing instructions on the stack.
Crucially, the stack is the only part of memory for which the runtime (including
malloc, loading, linking) will ever provide $\rwlx$ or $\rwl$ capabilities.
Additionally, our examples typically also assume some memory to store
instructions or static data. Another part of memory (called the heap) is
initially governed by malloc and at program start-up, no other code has
capabilities for this memory. Malloc hands out $\rwx$ capabilities for allocated
regions as requested (no $\rwlx$ or $\rwl$ permissions). For simplicity, we
assume that memory allocated through malloc cannot be freed.

>>>>

\textbf{Program start-up} We assume that the language runtime initializes the
memory as follows: a contiguous array of memory is reserved for the stack, for
which we receive a stack pointer in the register $r_\stk$. We stress that
the stack is not built-in, but merely an abstraction we put on this piece of the
memory. The stack pointer is local and has $\rwlx$ permission. Note that this
means that we will be placing and executing instructions on the stack.
Crucially, the stack is the only part of memory for which the runtime (including
malloc, loading, linking) will ever provide $\rwlx$ or $\rwl$ capabilities.
Additionally, our examples typically also assume some memory to store
instructions or static data. Another part of memory (called the heap) is
initially governed by malloc and at program start-up, no other code has
capabilities for this memory. Malloc hands out $\rwx$ capabilities for allocated
regions as requested (no $\rwlx$ or $\rwl$ permissions). For simplicity, we
assume that memory allocated through malloc cannot be freed.\footnote{In more realistic settings, reusing freed memory on a capability machine can be made safe by checking or enforcing that there are no dangling pointers to the freed memory, as implemented, for example, in CHERI-JNI~\citep{chisnall_cheri_2017}. }
